Syntactic realization with data-driven neural tree grammars

### 2016-10-09 paper/draft.tex
numbers added

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} & \textbf{After A*}  \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\% \\ \cline{2-4}
         &  Token       &  60.69\% & 55.56\% \\ \cline{2-4}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% \\ \cline{2-4}
         &  Token       &  82.65\% & 62.73\% \\ \cline{2-4}
\hline
\end{tabular}
\label{table:accresults}
\caption{Classification accuracy by supertag and its individual properties}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|p{1.5cm}|r|}
\hline
Model & Embedding & Beam Type & Accuracy \\ \hline
FERGUS & n.a. & n.a. & 74.9 \% \\
\hline \hline
Fergus-N & Convolution & $Top_{all}$  & 68.9\% \\ \cline{3-4}
         &             & $Best_{all}$ & 76.4\% \\ \cline{2-4}
         & Token       & $Top_{all}$  & XX\% \\ \cline{3-4}
         &             & $Best_{all}$ & XX\% \\ \cline{3-4}
\hline
Fergus-R & Convolution & $Top_{all}$  & 71.9\% \\ \cline{3-4}
         &             & $Best_{all}$ & 78.9\% \\ \cline{2-4}
         & Token       & $Top_{all}$  & XX \% \\ \cline{3-4}
         &             & $Best_{all}$ & XX \% \\ \cline{3-4}
\hline
\end{tabular}
\label{table:linresults}
\caption{Shown above as accuraccy is the percentage of tokens in the linearized strings that are in correct positions according to an edit distance measure.}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} & \textbf{After A*}  \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\% \\ \cline{2-4}
         &  Token       &  60.69\% & 55.56\% \\ \cline{2-4}
         & Minimal Token & 52.09\% & 54.18\% \\ \cline{2-4}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% \\ \cline{2-4}
         &  Token       &  82.65\% & 62.73\% \\ \cline{2-4}
         &  Minimal Token & 10.13\% & 19.66\% \\ \cline{2-4}
\hline
\end{tabular}
\label{table:accresults}
\caption{Classification accuracy by supertag and its individual properties}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{|l|p{3cm}|p{2.5cm}|r|}
\cline{3-4}
\multicolumn{2}{}{} & \multicolumn{2}{|c|}{Accuracy}   \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Top Scoring} & \textbf{Best Performance} \\ \hline
FERGUS & n.a. & \multicolumn{2}{|c|}{74.9  \%} \\
\hline \hline
Fergus-N & Convolution & 65.80 \% & 72.58 \% \\ \cline{2-4}
         & Token       & 65.52 \%  & 71.82 \% \\ \cline{2-4}
         & Minimal Token & 63.79 \% & 71.09 \% \\ \cline{2-4}
\hline
Fergus-R & Convolution & 68.22\% & 74.70\% \\ \cline{2-4}
         & Token       &  69.29 \% & 75.56\% \\ \cline{2-4}
         & Minimal Token &  58.23 \% & 65.04\% \\ \cline{2-4}
\hline
\end{tabular}
\label{table:linresults}
\caption{Shown above as accuraccy is the percentage of tokens in the linearized strings that are in correct positions according to an edit distance measure.}
\end{figure}
